Using an iterated block particle filter via \pkg{spatPomp}

### 2022-12-13 bm.Rnw
m-prof-R02 results

<<packages,include=F,echo=F,cache=F>>=
library("spatPomp")
library("gridExtra")
library("grid")
library("ggplot2")
library("xtable")
library("tidyverse")
library("cowplot")
library("knitr")
library("kableExtra")
stopifnot(packageVersion("pomp")>="4.1")
@

@@

%%%%%% iiiiiiii %%%%
<<bm-model,echo=T,eval=T>>=
library(spatPomp)
i <- 1
b <- bm2(U=4,N=switch(i,20,200),unit_specific_names="rho")
plot(b)
@

>>>>

<<packages,include=F,echo=F,cache=F>>=
library("spatPomp")
#library("gridExtra")
#library("grid")
library("ggplot2")
#library("xtable")
library("tidyverse")
#library("cowplot")
library("knitr")
#library("kableExtra")
stopifnot(packageVersion("pomp")>="4.1")
@

@@

%%%%%% iiiiiiii %%%%
<<bm-model,echo=T,eval=T>>=
library(spatPomp)
i <- 2
b <- bm2(U=4,N=switch(i,20,200),unit_specific_names="rho")
plot(b)
@
